Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-20 introduction.tex
Adding caption and discussion of Figure 2.
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1122 ccdd05d5-56c1-461a-bf98-85f6876523b4

\begin{table}[h]
\caption{\label{table:sky-localization-accuracy}Horizon distance, expected detection rate, and \SNR\ at merger for sources that produce an \SNR\ of 8 in all three detectors at time $t$ before merger.  The fifth and sixth columns show the minimum area of the 90\% confidence region before merger and at merger.}
\begin{center}
\begin{tabular}{rrrrrr}
\tableline\tableline
& horiz. & rate & final & \multicolumn{2}{c}{$A$(90\%) (deg$^2$)} \\
\cline{5-6}
$t$ (s) & (Mpc) & (yr$^{-1}$) & \SNR\ & early & final \\
\tableline
25.0 & 226 & 5 & 15.8 & 2893.2 & 1.8 \\
10.0 & 299 & 12 & 11.9 & 1150.6 & 3.6 \\
5.0 & 341 & 18 & 10.4 & 594.6 & 5.1 \\
1.0 & 401 & 29 & 8.9 & 153.9 & 7.5 \\
0.1 & 435 & 37 & 8.2 & 32.5 & 9.1 \\
0.0 & 445 & 40 & 8.0 & 9.6 & 9.6 \\
\tableline
\end{tabular}
\end{center}
\end{table}
%
\begin{figure}[h]
\plotone{figures/loc_in_time.pdf}
\caption{}
\end{figure}
%
\EM{} followup requires estimating the location of the \GW{} source. The
localization uncertainty is dominated by uncertainty in the time of arrival of
the \GW{}s, which is determined by the signal's effective bandwidth and \SNR{}
\citep{Fairhurst2009}.  Table~\ref{table:sky-localization-accuracy} shows the
minimum 90\% confidence area for a source that produces an \SNR\ of 8 in the
\LIGO\ detectors in Hanford, Washington, and Livingston, Louisiana, and, the
Virgo detector in Cascina, Italy, at a time $t$ before merger.  Also shown are
the final \SNR\ and 90\% confidence area at merger for the same source.
At 10~s before merger, the pre-merger 90\% confidence area is about $1150.6$~deg$^2$
(2.8\% of the sky) and at 1~s before merger is 153.9~deg$^2$ (0.37\% of the sky).
The confidence region shrinks quadratically in area as the overall amplitude of the
signal increases.

>>>>

\begin{table}[h]
\caption{\label{table:sky-localization-accuracy}Horizon distance, expected detection rate, and \SNR\ at merger for sources that produce an \SNR\ of 8 in all three detectors at time $t$ before merger.  The fifth and sixth columns show the minimum area of the 90\% confidence region before merger and at merger.}
\begin{center}
\begin{tabular}{rrrrrr}
\tableline\tableline
& horiz. & rate & final & \multicolumn{2}{c}{$A$(90\%) (deg$^2$)} \\
\cline{5-6}
$t$ (s) & (Mpc) & (yr$^{-1}$) & \SNR\ & early & final \\
\tableline
25.0 & 226 & 5 & 15.8 & 2893.2 & 1.8 \\
10.0 & 299 & 12 & 11.9 & 1150.6 & 3.6 \\
5.0 & 341 & 18 & 10.4 & 594.6 & 5.1 \\
1.0 & 401 & 29 & 8.9 & 153.9 & 7.5 \\
0.1 & 435 & 37 & 8.2 & 32.5 & 9.1 \\
0.0 & 445 & 40 & 8.0 & 9.6 & 9.6 \\
\tableline
\end{tabular}
\end{center}
\end{table}
%
\begin{figure}[h]
\plotone{figures/loc_in_time.pdf}
\caption{\label{fig:sky-localization-accuracy} Area of the 90\% confidence
region as a function of time for an exceptional source, where such a source is
defined to produce a signal with an \SNR\ of at least 27.4. These signals are
expected to be observed in the detectors once per year.  80~s, 35~s, 16~s, and
6~s before coalescence, such a signal will have accumulated an \SNR\ of 8, 12,
16, and 20, respectively. After merger, the minimum 90\% confidence area
shrinks to $0.82$~deg$^2$, shown by the dashed line.}
\end{figure}

\EM{} followup requires estimating the location of the \GW{} source. The
localization uncertainty is dominated by uncertainty in the time of arrival of
the \GW{}s, which is determined by the signal's effective bandwidth and \SNR{}
\citep{Fairhurst2009}.  Table~\ref{table:sky-localization-accuracy} shows the
minimum 90\% confidence area for sources that produces signals with an \SNR\ of
8 in the \LIGO\ detectors in Hanford, Washington, and Livingston, Louisiana,
and, the Virgo detector in Cascina, Italy, at a time $t$ before merger.  Also
shown are the final \SNR\ and 90\% confidence area at merger for the same
source.  For a source that accumulates an \SNR\ of 8 at a time 10~s before
merger, the pre-merger 90\% confidence area is about $1150.6$~deg$^2$ (2.8\% of
the sky) whereas a source that accumulates an \SNR\ of 8 at a time 1~s before
merger is 153.9~deg$^2$ (0.37\% of the sky).  The confidence region shrinks
quadratically in area as the overall amplitude of the signal increases.
Figure~\ref{fig:sky-localization-accuracy} tracks the minimum 90\% confidence
area as a function of time before coalescence for an \emph{exceptional source},
which is defined to be a source that produces a signal with an \SNR\ of at
least 27.4. Such sources are expected to be seen by the detectors on average
once per year. These sources would have minimum 90\% confidence areas of
$2250$~deg$^2$ and $270$~deg$^2$ at a time 30~s and 10~s before coalescence,
respectively.  After merger, the minimum 90\% confidence area shrinks to
$0.82$~deg$^2$.
